Estimating duration in the presence of misclassification

### 2023-12-15 biology-data.tex
Add concepts needed from todo list

\section{SARS-CoV-2 and COVID-19}

@@

\section{Assessment of Transmission and Contagiousness of COVID-19 in Contacts}

\section{Coronavirus (COVID-19) Infection Survey} \label{intro:sec:cis}

>>>>

Make sure I cover:
\begin{itemize}
  \item Relationship between Ct and viral load (and infectiousness?)
  \item Limit of detection
  \item The idea of being "detectable"? Check if/where/how I've used this concept in current version of text.
  \item 
\end{itemize}

@@

\section{Studies used in this thesis}

\subsection{Assessment of Transmission and Contagiousness of COVID-19 in Contacts}

\subsection{Coronavirus (COVID-19) Infection Survey} \label{intro:sec:cis}

### 2023-12-15 introduction.tex
Add concepts needed from todo list

\begin{itemize}
    \item Disease burden of pandemic and ongoing burden of COVID
    \item To mitigate its effects, need to understand incidence and transmission but cannot observe directly
    \item Importance of surveillance
    \item Expected future pandemics, methods should be reusable
\end{itemize}

@@

\begin{itemize}
    \item Most commonly used types of data: severe events (deaths/hospitalisations), widespread testing (pillar 2), 
    \item Advantages of designed surveys (REACT, CIS)
    \item Use of cohorts (ATACCC)
    \item Statistical modelling performed during the pandemic
\end{itemize}

>>>>

\begin{itemize}
    \item Disease burden of pandemic and ongoing burden of COVID
    \item To mitigate its effects, need to understand incidence and transmission but cannot observe directly
    \item Importance of surveillance objectives and concepts: incidence, transmission, basic reproduction number, effective reproduction number
    \item Expected future pandemics, methods should be reusable
\end{itemize}

@@

\begin{itemize}
    \item Most commonly used types of data: severe events (deaths/hospitalisations), widespread testing (pillar 2), 
    \item Advantages of designed surveys (REACT, CIS)
    \item Use of cohorts (ATACCC)
    \item Statistical modelling performed during the pandemic. Discuss broadly but especially focus on those using CIS or REACT. Discuss my contribution in this context.
\end{itemize}
